Adopting agile in the large: motivations, success factors and challenges

### 2013-10-29 journal/article.tex
Notes on inclusion criteria

>>>>

\subsection{Inclusion criteria}
- pitää olla systemaattinen
- pitää olla toistettava
==> Perustuu enimmäkseen siihen että on 2 tutkijaa toistamassa

There must be more discussion on transformation than a couple of sentences.
--> Esimerkkejä
--> Tasot 1--5 ??

Listing of not included topics. Discussion on these topics are considered not
providing insight to the research questions. Our goal is to address the research
questions, and specifically focus on analyzing the transformation process.
Not included topics:
--> Benefits of agile in general, problems with agile in general
--> Comparing agile and method X
--> Reporting on the current method, without consideration of how the method has
    been evolved (or transformed)
Tämän perusteella pitää siis kertoa itse prosessista: --> Kirjoita auki tämä
kriteeri paremmin.

% -----------------------
